The Migration of the Field Code

### 2016-02-12 talks/dh-working-group/dh-working-group.Rmd
Paragraph on harmony of the method

---
title: "The Migration of the Field Code"
author: "Kellen Funk and Lincoln Mullen"
date: "February 17, 2016"
output: tufte::tufte_handout
---

@@

@@

```{r, fig.fullwidth = TRUE}
a_cluster <- clusters %>% filter(cluster_id == 676) %>% `$`("doc")
sample_matrix <- sections[a_cluster] %>% 
  pairwise_compare(jaccard_similarity, progress = FALSE, directional = TRUE) %>% 
  round(2) 
sample_matrix[is.na(sample_matrix)] <- ""
knitr::kable(sample_matrix, align = "c", caption = "A sample similarity matrix")
```

>>>>

---
title: "The Migration of the Field Code"
author: "Kellen Funk and Lincoln Mullen"
output: tufte::tufte_handout
---

@@

We found out how the codes borrowed from one another by breaking the codes up into sections and comparing each section to every other section. We were justified in this approach because what we were doing was in essence repeating the process that nineteenth-century codifiers had taken. Newspapers and other observers mentioned the "the scissors and paste-pot " codes, and we have found in the archives codes which were marked up and edited by hand to be adopted for a different state. We think our method is successful because it mimics what we know to have happened by other historical methods.

@@

```{r, fig.fullwidth = TRUE}
a_cluster <- clusters %>% filter(cluster_id == 676) %>% `$`("doc")
sample_matrix <- sections[a_cluster] %>% 
  pairwise_compare(jaccard_similarity, progress = FALSE, directional = TRUE) %>% 
  round(2) 
sample_matrix[is.na(sample_matrix)] <- ""
knitr::kable(sample_matrix, align = "c", 
             caption = "A subset of the similarity matrix")
```
